### 2017-09-30 TF-vldb2018/sec-expt.tex

\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The description of the dataset can be found in the full version~\cite{fullvldb18}.

@@

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09}, and is firstly proposed for the team formation problem;
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
Among algorithms for \teamF, most of them including  \mindia and \denalk only compute the best team,
while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

We present our findings. In all the experiments, we set $k=10$, $r=2$, $h=3$, $(|V_{P}|,$ $|E_{P}|)$ to be (10,12),
and capacity bounds to be [1,10] by default.
When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
Aqll the findings on \youtube are reported in the Appendix.

\stitle{Exp-1: Efficiency of \optgrouprec}. We firstly evaluated the performance of \optgrouprec vs. \mindia, \minsumdis and \denalk.

Algorithms \mindia, \minsumdis and \denalk do not scale well on large graphs.
Indeed,  (1) \mindia and \minsumdis take more than $8$ hours to finish their preprocessing, \ie computing all-pair-shortest-paths, and (2) \denalk takes more than 24 hours even when $k=1$ on \citationd.
By contrast, \optgrouprec takes around 100 seconds on \citationd by default settings.
Hence, we report the effectiveness of these algorithms on a sampled data graph with $10,000$ nodes on \citationd only.
%We further evaluate the efficiency of \optgrouprec in the incremental experiments.
%\looseness=-1

\stitle{Exp-2: Effectiveness of \optgrouprec}.  We generated pattern graphs for \optgrouprec, and the corresponding queries (labels requirements) for \mindia, \minsumdis and \denalk, and checked the quality of matches returned by them. 
\looseness=-1

@@

Note that (a) and (b) are two traditional quality measures utilized by existing team formation algorithms.
Intuitively, $\eta_V(G_S, P)$ (resp. $\eta_E(G_S,P)$) measures how well $G_S$ meets the node capacity requirements (resp. structural constraints) in $P$, and their values fall in $[0, 1]$.

\etitle{(i) Impacts of $|V_{P}|$}. Varying the number $|V_{P}|$ of
nodes in $P$ from 4 to 16, we took the average value of top-$k$ teams found by  \optgrouprec, \mindia, \minsumdis and \denalk \wrt five quality measures.
The results are reported in Figures \ref{fig-exp-semantic-citation-diameter}-\ref{fig-exp-semantic-citation-link}.

Observe the following.
%
(1) In Fig.~\ref{fig-exp-semantic-citation-diameter}, the diameter of teams found by \optgrouprec is less than \mindia and \minsumdis, but the teams are with a small diameter, \eg less than \denalk, because of the ball restriction of \optgrouprec;
(2) in Fig.~\ref{fig-exp-semantic-citation-density}, the density of teams found by \optgrouprec is less than \denalk, while is higher than \mindia and \minsumdis;
(3) in Fig.~\ref{fig-exp-semantic-citation-capacity}, the node satisfiability of teams found by \optgrouprec, \ie 1.0 in all cases, is much higher than \mindia, \minsumdis and \denalk, \ie less than 0.2; and
(4) in Fig.~\ref{fig-exp-semantic-citation-link}, the teams found by \optgrouprec come with a higher edge satisfiability , \ie 1.0 in all cases, compared to less than 0.6 by \mindia, \minsumdis and \denalk.

@@

\warn{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and capacity satisfiability, and pertains a good team collaboration compatibility \wrt density and diameter.}

>>>>

\ni (3) We also used real-life dataset \youtube~\cite{youtubeWeb}. The detailed information of the dataset is available in the full version~\cite{fullvldb18}.

@@

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09},
\revise{and is firstly proposed for the team formation problem;}
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
Among algorithms for \teamF, \revise{most of them including  \mindia and \denalk only compute the best team,}
while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

We present our findings. In all the experiments, we set $k=10$, $r=2$, $h=3$, $(|V_{P}|,$ $|E_{P}|)$ to be (10,12),
and capacity bounds to be [1,10] by default.
When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
All the findings on \youtube are reported in the full version~\cite{fullvldb18}.

\stitle{Exp-1: Efficiency of \optgrouprec}. We firstly evaluated the efficiency of \optgrouprec vs. \mindia, \minsumdis and \denalk.
We generated pattern graphs for \optgrouprec, and the corresponding queries (labels requirements) for \mindia, \minsumdis and \denalk.

Algorithms \mindia, \minsumdis and \denalk do not scale well on large graphs.
Indeed,  (1) \mindia and \minsumdis took more than $8$ hours to finish their preprocessing, \ie computing all-pair-shortest-paths; 
and (2) \denalk took more than 24 hours even when $k=1$ on \citationd.
By contrast, \optgrouprec took around 100 seconds on \citationd by default settings.
Hence, we report the effectiveness of these algorithms on a sampled data graph with $10,000$ nodes on \citationd only.
%We further evaluate the efficiency of \optgrouprec in the incremental experiments.

\stitle{Exp-2: Effectiveness of \optgrouprec}. We then evaluated the efficiency of \optgrouprec vs. \mindia, \minsumdis and \denalk by checking the quality of matches returned by them.

@@

Note that (a) and (b) are two traditional quality measures utilized by existing team formation algorithms~\cite{GajewarS12,realTeamForm13,Lappas09,Kargar11}.
Intuitively, $\eta_V(G_S, P)$ (resp. $\eta_E(G_S,P)$) measures how well $G_S$ meets the node capacity requirements (resp. structural constraints) in $P$, and their values fall in $[0, 1]$.

\etitle{(i) Impacts of $|V_{P}|$}. Varying the number $|V_{P}|$ of
nodes in $P$ from 4 to 16, we took the average value of top-$k$ teams found by  \optgrouprec, \mindia, \minsumdis and \denalk \wrt four quality measures.
The results are reported in Figures \ref{fig-exp-semantic-citation-diameter}-\ref{fig-exp-semantic-citation-link}.

Observe the following.
(1) The diameters of teams found by \optgrouprec are comparable to those of \mindia and \minsumdis, which are in particularly designed to minimize the diameters, as shown in Fig.~\ref{fig-exp-semantic-citation-diameter}. This is ensured by the use of balls in \optgrouprec.
(2) The densities of teams found by \optgrouprec, though are smaller than \denalk which is specialized for maximizing team densities, are larger than \mindia and \minsumdis, as shown Fig.~\ref{fig-exp-semantic-citation-density}.
(3) The node satisfiability of teams found by \optgrouprec is much higher than \mindia, \minsumdis and \denalk, \eg 1.0 vs. no larger than 0.2 in all cases as in Fig.~\ref{fig-exp-semantic-citation-capacity}.
(4) The teams found by \optgrouprec come with a higher edge satisfiability , \ie 1.0 in all cases, compared to smaller than 0.6 by \mindia, \minsumdis and \denalk, as shown in Fig.~\ref{fig-exp-semantic-citation-link}.

%%
%\revise{(1) In Fig.~\ref{fig-exp-semantic-citation-diameter}, the diameter of teams found by \optgrouprec is less than \mindia and \minsumdis, but the teams are with a small diameter, \eg less than \denalk, because of the ball restriction of \optgrouprec;}
%(2) in Fig.~\ref{fig-exp-semantic-citation-density}, the density of teams found by \optgrouprec is less than \denalk, while is higher than \mindia and \minsumdis;
%(3) in Fig.~\ref{fig-exp-semantic-citation-capacity}, the node satisfiability of teams found by \optgrouprec, \ie 1.0 in all cases, is much higher than \mindia, \minsumdis and \denalk, \ie less than 0.2; and
%(4) in Fig.~\ref{fig-exp-semantic-citation-link}, the teams found by \optgrouprec come with a higher edge satisfiability , \ie 1.0 in all cases, compared to less than 0.6 by \mindia, \minsumdis and \denalk.

@@

\revise{These verify that \optgrouprec can effectively preserve structural and capacity constraints for top-$k$ team formation \wrt edge and capacity satisfiability, and pertains a good team collaboration compatibility \wrt density and diameter.}
